---
title: "Statistical Inference"
output: pdf_document
---

In this project is going to be reported a comparative study between the Mean and Variance of the Exponential distribution vs the Theoretical mean and Variance of it. 

Below is the code for a histogram of 40 random variables of an exponential distribution with lambda = 0.2 

```{r}
hist(rexp(40, 0.2), main="Exponential")
```

##1. Show the sample mean and compare it to the theoretical mean of the distribution.
Sample Mean versus Theoretical Mean: 

```{r echo=FALSE} 
layout(matrix(c(1,1,2,2), 2, 2, byrow = TRUE))
mne = NULL
for (i in 1 : 1000) mne = c(mne, mean(rexp(40, 0.2)))
hist(mne, main ="Mean 40 obs")
abline(v=5,lwd=3)

mne = NULL
for (i in 1 : 1000) mne = c(mne, mean(rexp(400, 0.2)))
hist(mne, main ="Mean 400 obs")
abline(v=25,lwd=3)

```

Theoretical mean is $1/lambda$ therefore mean $= 1/0.2 = 5$
If we encrease the number observations we can see the data more centered around the teorethical mean. 

## 2. Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.

Sample Variance versus Theoretical Variance:  

Theoretical variance is $1/lambda^2$ therefore variance= $1/0.2^2$

```{r echo=FALSE}
layout(matrix(c(1,1,2,2), 2, 2, byrow = TRUE))
vre = NULL
for (i in 1 : 1000) vre = c(vre, var(rexp(40, 0.2)))
hist(vre)

vre = NULL
for (i in 1 : 1000) vre = c(vre, var(rexp(400, 0.2)))
hist(vre)

abline(v=25,lwd=3)
```


# 3. Show that the distribution is approximately normal.

## Add a Normal Curve

```{r echo=FALSE} 
layout(matrix(c(1,1,2,2), 2, 2, byrow = TRUE))
mne = NULL
for (i in 1 : 1000) mne = c(mne, mean(rexp(40, 0.2)))
h<-hist(mne, main ="Mean 40 obs")
abline(v=5,lwd=3)
x<-mne
xfit<-seq(min(x),max(x),length=40) 
yfit<-dnorm(xfit,mean=mean(x),sd=sd(x)) 
yfit <- yfit*diff(h$mids[1:2])*length(x) 
lines(xfit, yfit, col="blue", lwd=2)

mne = NULL
for (i in 1 : 1000) mne = c(mne, mean(rexp(400, 0.2)))
h<-hist(mne, main ="Mean 400 obs")
abline(v=25,lwd=3)

x<-mne
xfit<-seq(min(x),max(x),length=40) 
yfit<-dnorm(xfit,mean=mean(x),sd=sd(x)) 
yfit <- yfit*diff(h$mids[1:2])*length(x) 
lines(xfit, yfit, col="blue", lwd=2)

```

The Central Limit Theorem states that a distribution of idd variables becomes that of a standardnormal as the sample size increases.

 if we see plots above we can se that in the increase of the samples. The Average tend to center at its real value. 


