---
title: "ToothGrowth"
output: pdf_document
---


##1. Load the ToothGrowth data and perform some basic exploratory data analyses 
```{r}
data(ToothGrowth)
str(ToothGrowth)

boxplot(len~supp,d=ToothGrowth)
plot(ToothGrowth$dose,ToothGrowth$len) 
plot(ToothGrowth$sup,ToothGrowth$len)
```


##2. Provide a basic summary of the data.
```{r}
summary(ToothGrowth)

tapply(ToothGrowth$len,ToothGrowth$sup,mean)
```


##3 .Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.
```{r}
#T test for the difference in mean in pig with VC and OJ. 
VC<-subset(ToothGrowth,supp=='VC')
OJ<-subset(ToothGrowth,supp=='OJ')

Sx<-var(VC$len)
Sy<-var(OJ$len)

sp<-sqrt((29*Sx^2 + 29*Sy^2)/(30+30-2))
#Confidence interval for difference in mean of pigs with VC and OJ. 
20.66333-16.96333+c(-1,1)*qt(.975,58)*sp*(1/30 + 1/30)^0.5

```
$O$ is in The confidence interval is in so with a certainty of 95% there is no Statistical difference between the pigs with OR and the pigs with VC.

##4. Conclusion and assumptions. 
Conclusion: 
Supplement type does not make a statistical difference in the lenght of pigs.

Assumptions are : 
*Data from pics is iid normal distribuited. 
*Pigs with OJ and pigs with VC are from independent groups.

